\documentclass[12pt,letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{graphicx}

\pagestyle{fancy}

\author{Andrew Rosen}
\title{Regex}

\begin{document}
    
    
    
    \maketitle
    
    
    \begin{abstract}
    	This is extra credit and an incentive for you to learn Regex.  Each page is worth 5 points.
    \end{abstract}
    
    \section{Regex Dictionary}
    For this section, I want you to answer questions about the dictionary file \texttt{words.txt}.  If you're using a Unix system, feel free to use the dictionary file included on your computer.
    Some words begin with capital letters!
    Please include each regex with your answer.
    \begin{enumerate}
    	\item I like animals.  How many words contain the word 'cat' or 'dog' in them?
    	\item Four letters words are supposedly naughty.  How many four letter words are there?
        \item Do more words end in ``ing'' or ``ion?''
        \item How many words contain a ``q'' not immediately followed by a ``u.''
        \item How many words have no vowels?
        \item How many words with two vowels \textbf{in a row} are there?
        \item How many words with at least two vowels are there?  The vowels need not be adjacent, like in the previous problem.
    \end{enumerate}
    
    
    If you are having trouble, please see this \href{http://www.regexr.com/}{link}.
    
    \newpage
    \section{More Regex}
    
    \begin{enumerate}
    	\item What is the difference between \texttt{.* }and \texttt{.*?} ?
    	\item  How would you write a regex that matches the full name of someone
    	whose last name is Nakamoto? You can assume that the first name that
    	comes before it will always be one word that begins with a capital letter.
    	The regex must match the following:
    	\begin{itemize}
    		\item 'Satoshi Nakamoto'
    		\item 'Alice Nakamoto'
    		\item 'RoboCop Nakamoto'
    	\end{itemize}
    	but not the following:
    	\begin{itemize}
    		\item 'satoshi Nakamoto' (where the first name is not capitalized)
    		\item 'Mr. Nakamoto' (where the preceding word has a nonletter character)
    		\item 'Nakamoto' (which has no first name)
    		\item 'Satoshi nakamoto' (where Nakamoto is not capitalized)
    	\end{itemize}
    
    	\item Create a regex which matches the strings twenty, twenty-one, twenty-three,\dots,ninety-nine
    \end{enumerate}

\end{document}
